Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
claen sectino 3

\paragraph{Structure.}
In section
\ref{section:pnets} we give a description and a formal definition of
the pNet model, as found in previous publications. Then in
\ref{section:examples} we present a simple example that will
illustrate the rest of the paper.
Section \ref{section:op-semantics} recalls the operational semantics
of pNet, including its structural rules
%, and a sketch of the algorithm
%to compute such semantics, but also explains the enhancement we have
%done to these definitions
.
Section \ref{section:implementation} explains in details our
implementation within the Vercors platform, and shows the full result of
the semantic computation on the running example.
Finally we conclude and discuss perspectives in section
\ref{section:conclusion}.

@@

In this paper, we use an example inspired from LOTOS, to illustrate
the main features of pNets and the way we deal with them in the symbolic
semantics, and in the satisfiability checking. 
\QIN{
Meanwhile, 
the formula using operators from CCS can also be encoded into a pNet and 
conducted with the same things.
}

\subsection{LOTOS Formula Example}

\begin{figure}[h]
  \centerline{\includegraphics[width=10cm]{XFIG/LOTOSFormula.eps}}
  \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
\end{figure}

We choose the expression \texttt{P>>(acc(v);Q)}, that includes the
Enable and Prefix 
operators of the LOTOS language. For the readers not familiar with
Lotos, the pNet encodings here should be sufficient to understand the
Enable operator semantics.
In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using pNets. 
This pNet is composed of: a toplevel node PN1 encoding the Enable
operator, with its controller (pLTS) C1; a hole representing the
process variable P; another node PN2 representing the Prefix
operator, with its controller C2, and its hole Q.

@@

\TODO{I'm thinking about moving this second example to section 5...}
\QIN{[This CCS example is removed.]}

@@

\TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}

>>>>

\paragraph{Structure.}
In section
\ref{section:pnets} we give a description and a formal definition of
the pNet model, as found in previous publications. Then in
\ref{section:examples} we present a simple example that will
illustrate the rest of the paper.
Section \ref{section:op-semantics} recalls the operational semantics
of pNet, including its structural rules.
%, and a sketch of the algorithm
%to compute such semantics, but also explains the enhancement we have
%done to these definitions
Section \ref{section:implementation} explains in details our
implementation within the Vercors platform, and shows the full result of
the semantic computation on the running example.
Finally we conclude and discuss perspectives in section
\ref{section:conclusion}.

@@

 \begin{figure}[t]
   \centerline{\includegraphics[width=10cm]{XFIG/LOTOSFormula.eps}}
   \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
 \end{figure}

In this paper, we use an example inspired from LOTOS, to illustrate
the main features of pNets and the way we deal with them in the symbolic
semantics, and in the satisfiability checking. 
%% \QIN{
%% Meanwhile, 
%% the formula using operators from CCS can also be encoded into a pNet and 
%% conducted with the same things.
%% }
%% \subsection{LOTOS Formula Example}
We choose here the expression \texttt{P>>(acc(v);Q)}, that includes the
Enable and Prefix 
operators of the LOTOS language. For the readers not familiar with
Lotos, the pNet encodings here should be sufficient to understand the
Enable operator semantics.
In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using pNets. 
This pNet is composed of: a toplevel node PN1 encoding the Enable
operator, with its controller (pLTS) C1; a hole representing the
process variable P; another node PN2 representing the Prefix
operator, with its controller C2, and its hole Q.

@@

%% \TODO{I'm thinking about moving this second example to section 5...}
%% \QIN{[This CCS example is removed.]}

@@

%% \TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
